%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\makeatletter\@openrightfalse
\chapter{Campaign}
\@openrighttrue\makeatother


\section{Check-In}

As they arrive for the opening night briefing, players will be asked
to complete a simple, short questionnaire:

\begin{itemize}
\item \emph{Are you more focused on gameplay than on the hobby aspects of miniatures?}
\item \emph{Do you regularly or often play in tournaments?}
\item \emph{Do you consider yourself a strong competitive player?}
\item \emph{Have you played in a Ground Tournament (GT) or similar
    level of competitive event in the past year?}
\item \emph{Does your (standalone) army include more than one superheavy vehicle or gargantuan creature?}

\item \emph{Is your (standalone) army comprised of more than a single detachment or formation+}
\end{itemize}

(again, this is a draft)


At the start of the opening night campaign briefing, players will be asked
to 

As players check in at this year's NOVA, they'll be asked to complete and submit a quick
questionnaire.  This will ask just a handful of simple questions such as


``'' or ``Do you consider
yourself a regular top contender in your local tournaments

Opening night (Thursday, Sept 1st) will begin with a quick telling of
the background story for the campaign and how it will progress
mechanically and narratively.  

After players have all checked-in at NOVA, if necessary

At the opening night campaign briefing, each player will be asked to
complete a quick questionnaire card.


On opening night

For the first round opening 
