%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\section{Civilians}

The campaign's conflict does not occur in a vacuum---all games will
include civilians to be slaughtered or saved as the players wish.
Before selecting deployment zones, roll off and alternate in that
order placing~3 civilians each (both teammates do so in doubles
games).  They must be placed outside both deployment zones, at least
12'' from each other and at least 6'' from table edges.

  \begin{center}    
  \begin{tabular}[t]{O{0.75in}ccccccccF{.25in}F{1in}E{2in}}
    & {\bf WS} &  {\bf BS} & {\bf S} & {\bf T} & {\bf W} & {\bf I} & {\bf A} & {\bf Ld} & {\bf Sv} & {\bf Type} & {\bf Special Rules}\\
\hline
    {\bf Civilian} & 1 & - & 2 & 2 & 1 & 3 & - & 4 & 6+ 6++ & Infantry & Neutral NPC\\
  \end{tabular}
  \end{center}

  \label{rule:neutral-npc}
  \hfill
  \begin{minipage}{6in}
    \missionsubheading{Neutral NPC.} Units of either player may join a
    neutral NPC following the rules for independent characters.  Once
    joined, the NPC is considered a model of that player's army until
    the unit is eliminated or detaches from the NPC.  It may embark in
    transports and buildings while part of a unit; a unit cannot
    detach while embarked and leave an NPC behind embarked.  The NPC
    never moves on its own, including to join or leave units.  Players
    may shoot and assault unattached NPCs as though they were enemy
    models.  Models in an attached unit may Look Out, Sir! to protect
    the NPC from wounds allocated to it, and the NPC may be used to
    Look Out, Sir! and protect another model.  NPCs are not scoring
    and never count toward any mission objectives, including but not
    limited to kill points and controlling objective markers, even
    while joined to a unit.
  \end{minipage}
  \hfill\hbox to 0pt{}


\missionheading{Fame and Infamy}

The fate of civilians critically determines each army's reputation,
measured by the number of points earned toward fame and infamy.  Both
of these are tracked, and the final leader for each awarded a small
prize.

\missionsubheading{Wanton Slaughter.}  Any attack that eliminates a
civilian earns the attacking player~2 infamy points.

\missionsubheading{Meat Shields.}  If a civilian joined to a unit is
the first model removed when the unit is targeted by shooting, psychic
attacks, or in a round of close combat, or if a civilian is removed
after being used to Look Out, Sir! for another model in an attached
unit, then the unit's player earns~1 infamy point.

\missionsubheading{Heroes of the People.}  At game end, each civilian
attached to a unit earns that player~4 fame points.

\missionsubheading{Safe Haven.}  At game end, each unattached civilian
wholly inside a player's deployment zone earns that player~2 fame
points.

\missionsubheading{Black and White.}  Fame and infamy are exclusive of
each other.  After each match, only the greater of the player's fame
or infamy will be added to their respective running total, after
subtracting the lesser.
