%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\makeatletter\@openrightfalse
\chapter{Gameplay Rules}
\@openrighttrue\makeatother

This section defines the basic gameplay rules applied in the 40k Narrative.

\section{Core Rules}

The following rules apply to all games in the NOVA 40k Narrative.

\paragraph{Time Limits.}
Matches are scheduled for~2.5 hours, but players may take more time as
long as they mutually agree to do so.  Please discuss and agree to
play long or not at the start of each match, or at least well before
the time limit, so that there are no assumptions or mismatched
expectations.  This flexibility ensures that players may participate
in seminars and other NOVA events without hindering their Narrative
experience, but have the option to play at a relaxed pace if they have
no schedule constraints.  Results must be submitted at least half an
hour before the next activity on the Narrative schedule.

\paragraph{Invisibility.}
The Invisibility psychic power is amended to be:

\begin{center}  
\begin{tabular}{L{6in}}
\arrayrulecolor{LineColor}\hline\\
  \emph{Invisibility} is a blessing that targets a single friendly unit
  within 24". While the power is in effect, enemy units shooting at the
  target unit do so at BS 1, and in close combat will only hit models of
  the target unit on To Hit rolls of 5+.\\
\\
\arrayrulecolor{LineColor}\hline\\
\end{tabular}
\end{center}

\paragraph{Rerollable 2+ Saves.}
For any failed 2+ save that may be rerolled, the reroll only succeeds on a 4+.

\paragraph{Objective Markers.}
Standard objective placement constraints apply in setting up a game
unless noted otherwise by a specific mission.  Objective markers may
be controlled or contested by models/units up to 3" horizontally from
the side edge of the marker and 6" vertically from its bottom
face. Objective markers should all be the same size (typically
equivalent to a 40mm base).


\section{Team Rules}

The rules in this section apply to team games in the 40k Narrative.

\paragraph{Separate Allies.}
All players in a team field their strike force lists as separate
armies. Regardless of factions, teammates consider their
  partners' units and models to be allies of convenience to their own
  army.  In addition, all players on a team nominate a warlord for
themselves as usual.
%, thus a doubles pair would have two warlords in play.

\paragraph{Warp Storm Table.}
Results rolled by a player on the Warp Storm table (\emph{Codex: Chaos
  Daemons}) do not affect their teammates' armies and models unless
specifically dictated by the table, i.e., other Chaos Daemons or
marked Chaos Space Marines.

\paragraph{Psychic Phase.}
In the psychic phase, a single D6 is rolled by the current team to
determine the base warp charge from which each player on both teams
generates their own individual pools, applying the usual rules to
their own models. Players all use their own warp charge pool;
teammates cannot combine or share warp charge. Any opposing player
with models on the table may attempt to deny the witch, caveat that if
a specific unit of enemy models is targeted, their player alone may
attempt to block the spell.

\paragraph{Single Army.}
For all other gameplay purposes the combined forces of a team are
considered a single army comprised of multiple detachments, and the
team considered a single player for all rules except when specifically
distinguished by the missions here. How units belonging to different
players in a team interact are thus governed by the rules for allies
of convenience, on page 126 of the main \emph{Warhammer 40,000}
rulebook.  Being a single army also entails a number of other rules,
including:
\begin{itemize}
\item Units may not shoot at close combats even if none of their player's
units are engaged.

\item Teams are not eliminated unless there are no models of any member on
the table.
\end{itemize}



\section{Startup Sequence}

The start of each game proceeds as follows unless the mission notes
otherwise:

\begin{enumerate}\shortlist
\item Clarify terrain and mission rules

\item Share and clarify army lists

\item Determine warlord traits, then psychic powers, and then other
  pre-game effects and choices

\item D6 roll off to select deployment zones

\item Place primary objective markers

\item D6 roll off to choose first or second deployment

\item Deploy main armies in that order

\item Deploy any Infiltrators (pg. 167)

\item Secretly choose and record secondary objectives from the options
  listed for the mission

\item Make any Scout redeployments (pg. 171)

\item Reveal secondary objectives and any related selections or marker
  placements as directed

\item First to deploy chooses to play first or second

\item Seize the Initiative roll, if desired and permitted

\item \emph{Battle!}
\end{enumerate}
