%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\makeatletter\@openrightfalse
\chapter{Missions}
\@openrighttrue\makeatother

This chapter presents the missions used throughout the campaign.

\section{Scoring}

Match results are determined by scoring primary, secondary, and
tertiary objectives as given for the mission.  No more than a total
of~9 victory points may be earned for primary objectives,~6 for
secondary objectives, and~5 for tertiary objectives, for a total of no
more than~20 victory points possible in a match.  The winner is the
player with more victory points at game end, or a draw if they earned
equal amounts.
  
\section{Standard Mission Rules}

The following special rules are applied to each mission unless noted
otherwise.

\paragraph{Easy Recon.}  Players add~+1 to their roll to
choose first or second deployment for each superheavy vehicle or
gargantuan creature in the opposing army.

\paragraph{Reserves.} As defined on page~135 of the main
\emph{Warhammer 40,000} rulebook.

\paragraph{Seize the Initiative.} As defined on page~132 of
the main \emph{Warhammer 40,000} rulebook.

\paragraph{Variable Game Length.} As defined on page~133 of
the main \emph{Warhammer 40,000} rulebook.

\paragraph{All In.}  Units/models in reserve at game end count
as completely destroyed/removed as a casualty.

\section{Tertiary Objectives}

The following common tertiary objectives apply in each mission.
\underline{At most~5 total victory points may be}
\underline{earned by a player across all of the tertiary objectives.}

\begin{itemize}
\item \textit{Victory Through Attrition.}  Score~1 victory point for
  every~2 unsaved hull points or wounds suffered by an opposing
  superheavy vehicle or gargantuan creature through any means,
  including explosions and other indirect effects.  These points are
  earned at the end of any phase in which such damage occurs, and thus
  include any repaired or regenerated later.

\item \textit{Slay the Warlord.}  If your opponent's Warlord or a Lord
  of War character of theirs has been removed as a casualty or is
  falling back at the end of the game, score~2 victory points.

\item \textit{Linebreaker.}  Score~2 victory points if a model from
  any friendly scoring unit is completely within 12'' of your
  opponent's table edge.

\item \textit{First Blood.}  As defined on page~133 of the main
  \emph{Warhammer 40,000} rulebook.

\item \textit{Special Conditions.}  Any unit, faction, formation, or
  other special rules granting victory points to either player are
  considered tertiary objectives and are included within the~5 point
  cap.
\end{itemize}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\input{mission-list}
\newcommand{\missiontitle}[1]{\clearpage\section{#1}}
\newcommand{\missionheading}[1]{\subsection{#1}}
\newcommand{\missionsubheading}[1]{\paragraph{#1}}
\setlength{\headingspacing}{0pt}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\input{missions/brushfire}
