%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\makeatletter\@openrightfalse
\chapter{Awards}
\@openrighttrue\makeatother

The NOVA 40k Narrative is a casual, team-oriented campaign, not a
tournament.  The focus is on the alliances and the storyline
constructed.  However, some individual achievements will be
recognized.

\section{Fame and Infamy}

Fame and Infamy will be tracked for each player based on those points
earned in each round.  Remember that within each mission these score
exclusively of each other, as described previously.

\section{Standings}

Players will also be scored individually and ranked within their alliance
by summing match results, sportsmanship, and craftsmanship.

\subsection{Match Results}

Players will accumulate their victory points earned in each match.  Up
to~20 victory points are available in each round, as described in the
previous pages.  Partners will all receive the same score in team
games.

\subsection{Sportsmanship}

Each round players submit a sportsmanship score for their opponent.
By default players receive~5 sportsmanship points each round, from
which points are docked by the following rubric.

% \emph{\bf 
\bigskip
\centerline{\begin{tabular}{L{5in}c}
\rowcolor{LineColor} {\color{white}\bf Negative Behavior} & {\color{white}\it\bf Penalty}\\
Openly hostile or rude & -3 pts\\
\rowcolor{LightGray}Unnecessarily competitive in army list or attitude & -2 pts\\
Sloppy with measuring, moving, line of sight, or dice & -2 pts\\
\rowcolor{LightGray}Unreasonably late, overly slow play, or too inattentive & -1 pts \\
Significantly unfamiliar with rules or made too many mistakes & -1 pts\\
\rowcolor{LightGray}Not prepared with clear, readable, typed army lists & -1 pts\\
\end{tabular}}

\bigskip%
Partners will all receive the same score in team games.  Note that it
is perfectly acceptable for players to score maximum sportsmanship
points. Sportsmanship scores should be seen as free points, with poor
sportsmanship penalized, rather than an award for for minimally
acceptable behavior.

\subsection{Craftsmanship}

NOVA Open painting judges will evaluate the technical craftsmanship
present in each army to produce a painting and appearance score.  The
standardized NOVA Open painting and appearance judging process and
rubrics are available from the NOVA Open website. In short, the judges
rank armies into four tiers, from Tier 4, Ineligible (not painted), to
Tier~1, Work of Art (masterfully painted). Most armies wind up in
Tier~2, Tournament Standard, and some in Tier 3, Tabletop Mnimum
(essentially the classic ``3-color minimum''). The few armies that
make it into Tier~1 are evaluated by the judges in more detail and
given an additional NOVA Open painting score ranging from~-12 to~12.

\clearpage
Those tiers and NOVA Open painting score will be mapped to 40k
Narrative scoring as in the following table, for a total possible
craftsmanship score of~30 points.

\begin{center}  
\begin{tabular}{ccc}
\rowcolor{LineColor}\textbf{\color{white} Tier } & \textbf{\color{white} Description } & \textbf{\color{white} 40k Narrative Score }\\
Tier 1 & Work of Art & 24 + (judges' score / 2), rounding up\\
\rowcolor{LightGray} Tier 2 & Tournament Standard & 17\\
Tier 3 & Tabletop Minimum & 9\\
\rowcolor{LightGray} Tier 4 & Ineligible & 0\\
\end{tabular}
\end{center}

\section{Awards}

The following will be recognized based on individual overall standings:

\begin{center}
\begin{tabular}{ccc}
\rowcolor{LineColor}\textbf{\color{white} Rank} & \textbf{\color{white} Virtue} & \textbf{\color{white} Humanity}\\
1 & Paragon of the Virtue & Hero of the Free\\
2 & Exemplar of the Virtue & Commander of the Free\\
3 & Champion of the Virtue & Lieutenant of the Free\\
\end{tabular}
\end{center}

Ties will be broken by sportsmanship, then
win/loss/draw bracket, and then strength of schedule.

\bigskip%
Fame and Infamy titles will awarded to the players with the most
points scored in each across both alliances.  Ties will be broken by
sportsmanship and then overall standings.

\bigskip%
The player with highest craftsmanship score will also be recognized as
the event's bleading artist.  Ties will be broken by sportsmanship and
then overall standings.
