\documentclass{40k}

\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{ragged2e}

\input{resourcecard.tex}

\begin{document}
\centering

\clearpage
\squelchbackground
\begin{landscape}
\vspace*{-15pt}


\newcommand{\coverta}{%
\renewcommand{\scorematrix}{%
\centerline{\Large\fontfamily{ptm}\selectfont Backfield Reconnaissance}
\bigskip\small

After both players deploy, secretly select one friendly unit,
identifying it in writing on this card.  At game end you achieve this
covert mission if that unit scores Linebreaker, earning 9 points for
your alliance toward your battle zone.


\bigskip%
\bigskip%
\bigskip%
\bigskip%
\bigskip%
\bigskip%
\begin{minipage}{1.0\linewidth}\centering
  \checkbox \hspace{1em} Mission accomplished!\\
\bigskip%
Your Name: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\\
\bigskip%
Opponent's Signature: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{minipage}
}%
\drawscorecard
}

\newcommand{\covertb}{%
\renewcommand{\scorematrix}{%
\centerline{\Large\fontfamily{ptm}\selectfont Personnel Observation}
\bigskip\small

After both players deploy, secretly select one friendly character and
one enemy character, identifying them in writing on this card.  If at
any point your character is within 6'' of the enemy character, you
achieve this mission and earn 9 points for your alliance toward
your battle zone.


\bigskip%
\bigskip%
\bigskip%
\bigskip%
\bigskip%
\vspace{-2pt}%
\begin{minipage}{1.0\linewidth}\centering
  \checkbox \hspace{1em} Mission accomplished!\\
\bigskip%
Your Name: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\\
\bigskip%
Opponent's Signature: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{minipage}
}%
\drawscorecard
}

\newcommand{\covertc}{%
\renewcommand{\scorematrix}{%
\centerline{\Large\fontfamily{ptm}\selectfont HVT Capture}
\bigskip\scriptsize

Before any deployment, publicly identify a friendly unit as leading a
covert mission.  Reveal this card at any time to grant that unit the
Tank Hunters, Monster Hunters, Precision Shots, and Precision Strikes
USRs.

\hspace{1em} After deployment concludes, secretly select as the target
of this mission one enemy vehicle, monstrous or gargantuan creature,
or character with at least 3 wounds, and identify it in writing
\emph{on your scoresheet.}

\hspace{1em} Immediately upon the target losing its final wound or
hull point, you earn 3 points for your alliance toward your battle
zone.  In addition, place a casualty marker at the target's last
location.  At the end of your first turn in which you control that
marker, you earn 3 points for your alliance.  If you control the
marker at game end you earn an additional 3 points for your alliance.

\hspace{1em} The unit leading the mission does not have to itself
eliminate the target or control the casualty marker.

\small
\bigskip%
\vspace{-2pt}%
\begin{minipage}{1.0\linewidth}\centering
Points earned: \underline{~~~~~~~~~~~~~}\\
\smallskip%
Your Name: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\\
\smallskip%
Opponent's Signature: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{minipage}
}%
\drawscorecard
}

\newcommand{\covertd}{%
\renewcommand{\scorematrix}{%
\centerline{\Large\fontfamily{ptm}\selectfont Search}
\bigskip\scriptsize

After deployment concludes, place 3 search markers in separate terrain
pieces outside your deployment zone.

\hspace{1em} At the end of your first turn in which you control any
search marker, you earn 4 points for your alliance toward your battle
zone.  In addition, randomly select one of the two other search
markers.  At the end of your first turn in which you control that
marker you earn 5 points for your alliance toward your battle zone.

\hspace{1em} If you control multiple search markers at the end of the
first turn in which you do so, you earn 9 points for your alliance and
do not roll to select another.

\small
\bigskip%
\bigskip%
\bigskip%
\bigskip%
\smallskip%
%\vspace{-2pt}%
\begin{minipage}{1.0\linewidth}\centering
Points earned: \underline{~~~~~~~~~~~~~}\\
\bigskip%
Your Name: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\\
\bigskip%
Opponent's Signature: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{minipage}
}%
\drawscorecard
}

\noindent%
\covertd%
%
%
\hfill%
%
%
\covertd%
%
%
\hfill%
%
%
\covertd

\vfill

\covertd
%
\hfill%
%
\covertd
%
\hfill%
%
\covertd

\end{landscape}
\clearpage
\restorebackground
\end{document}
