%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Brushfire}

\smallskip
\teaser{Both sides fight to control ground amid the sudden open rebellion.}
\bigskip

\begin{tablesetup}

  \dawnofwar

  \smallskip%
  Place one primary objective marker at table center.  Beginning with
  the winner of a~D6 roll off, both players alternate placing one
  primary objective marker and then a second, for a total of~5 on the
  board once setup is complete.  These markers may be placed anywhere
  on the board within the standard rules.
\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}
\nightfighting
\end{missionrules}


%%----------------------------------------------
\begin{scoring}
  
\begin{primaries}

  Before any Scout redeployments, both players secretly choose one of
  the following primary scoring mechanisms for themselves:

  \begin{itemize}
  \item {\textit{Continuous.}} Beginning with Turn~2, score~1 victory
    point at the end of each of your player turns for each primary
    objective marker you control.
  
  \item {\textit{End Game.}} At game end, score~3 victory points for
    each primary objective marker you control.
  
  \end{itemize}

  This selection is declared along with the choice of secondary
  objective, below, after Scout redeployments.  Remember that
  \underline{no more than 9 victory points may be earned toward
    primary objectives}.

\end{primaries}

\begin{secondaries}
  \interrogation
  \civilians
%  \breaktheirback
%  \securepositions
\end{secondaries}

\end{scoring}
