%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Convoy\single}

\teaser{The supplies in this vehicle are desperately needed on the
  front line, see that they get through!}

\begin{tablesetup}

  \dawnofwar

  \smallskip%
  Before any deployment begins, each player gains a Bulldog Transport
  for their army:

  \begin{center}    
  \begin{tabular}[t]{rcccccL{3in}}
    & {\bf BS} &  {\bf F} & {\bf S} & {\bf R} & {\bf HP} & {\bf Special Rules}\\
    {\bf Bulldog Transport} & - & 11 & 11 & 10 & 3 & Smoke Launchers (4), Transport (6), Advanced Repair Systems, Tank\\
  \end{tabular}
  \end{center}

  \hfill
  \begin{minipage}{6in}
    \missionsubheading{Advanced Repair Systems.} If the vehicle is
    immobilized at the start of its movement, roll a~D6.  On a~4+ it
    is no longer immobilized, and may immediately move as normal.  It
    does not regain any hull points lost.  If the roll is failed then
    the vehicle may move 3'' as it attempts to lurch back to life.
    This roll may be taken every turn until successful.
  \end{minipage}
  \hfill\hbox to 0pt{}

  \bigskip The Bulldogs may not be held in reserve and must deploy
  wholly within 6'' of the player' table edges.  They do not count
  toward any secondary objective but do count toward First Blood and
  Linebreaker.
\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

\bigskip
There are no rules specific to this mission.

\end{missionrules}


%%----------------------------------------------
\begin{scoring}  
\begin{primaries}

  At the end of the first movement phase in which a player's Bulldog
  is fully within their opponent's half of the table, the controlling
  player gains~2 victory points.  At the end of the first movement
  phase in which a player's Bulldog is fully within their opponent's
  deployment zone, the controlling player gains~1 victory point.  At
  game end, players earn~3 victory points if their Bulldog has not
  been destroyed.  They also earn~1 victory point for each hull point
  removed from their opponent's Bulldog.

%\underline{No more than~9 victory points may be earned by primary objectives.}

\end{primaries}
\end{scoring}
