%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Supply Depot\single}

\teaser{Cut off and all alone, your army will have to improvise its
  own supplies!}

\begin{tablesetup}

  \vanguardstrike

  \smallskip%
  After selecting deployment zones, players roll off and in that order
  alternate placing a supplies marker in their deployment zone, in
  their opponent's deployment zone, and then in neither deployment
  zone.  Supplies markers act as objective markers.
\end{tablesetup}

%%----------------------------------------------
\begin{missionrules}

  \missionsubheading{Ransack.}{Immediately upon the first time a
    walker or non-vehicle model moves into base contact with a
    supplies marker, determine its victory points value by rolling on
    the following table:

    \begin{center}      
      \begin{tabular}{ccc}
        \rowcolor{LineColor} {\color{white}\bf D6} & {\color{white}\bf Value} & {\color{white}\bf In Play} \\
        {\bf 1} & {\bf 4} & $\Box$ \\
        {\bf 2} & {\bf 3} & $\Box$ \\
        {\bf 3} & {\bf 3} & $\Box$ \\
        {\bf 4} & {\bf 2} & $\Box$ \\
        {\bf 5} & {\bf 2} & $\Box$ \\
        {\bf 6} & {\bf 1} & $\Box$ \\
      \end{tabular}
    \end{center}

    Check off the rolled entry as ``In Play.'' That entry cannot be
    selected again; re-roll the die if it comes up in a future ransack
    roll.

    At game end follow the same process in random order for any
    markers that are controlled but whose value has not been
    determined, i.e., they are controlled but have not been in
    contact, or have been contacted only by non-walker vehicles.}

\end{missionrules}


%%----------------------------------------------
\begin{scoring}  
\begin{primaries}

  At game end each supplies marker is worth its victory point value
  determined by the ransack rule above.  \underline{Remember that no
    more than~9 victory points may be earned toward primary scoring.}

\end{primaries}
\end{scoring}
